%% Copyright (C) 2024 Nuno David Lopes.-----------------------------------
%%
%% e-mail: nuno.lopes@isel.pt
%%
%% First added:  2014-05-02
%% Last changed: 2024-06-18


\documentclass[10pt,a4paper,sans]{moderncv} % Note: Use XeLaTeX or LuaLaTeX for academicons compatibility
\moderncvstyle{classic}
% moderncv themes
%\moderncvstyle{casual}       % style options are
                              %'casual' (default), 'classic', 'oldstyle' and 'banking'


\moderncvcolor{blue} % color options are 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}   % to set the default
                                             % font; use '\sfdefault'
                                             % for the default sans
                                             % serif font, '\rmdefault'
                                             % for the default roman
                                             % one, or any tex font name

%\nopagenumbers{}   % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage{lmodern}
\usepackage[portuguese]{babel}

%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage{lastpage}
\rfoot{\addressfont\itshape\textcolor{gray}{\thepage\ de \pageref{LastPage}}}

% personal data
\name{Nuno}{Lopes}

\title{Curriculum Vit\ae}  % optional, remove / comment the line if not wanted

%\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%\address{}{}{1700-018 Lisboa, (Portugal)}
\phone[mobile]{+351 916833519} % optional, remove / comment the line if
                               % not wanted; the optional "type" of the
                               % phone can be "mobile" (default), "fixed" or "fax"
\email{nuno.lopes@isel.pt}     % optional, remove / comment the line if not wanted
%\homepage{http://ptmat.fc.ul.pt/$\sim$ndl} % optional, remove / comment
%the line if not wanted
\extrainfo{https://github.com/ndlopes-github\\
ORCID: 0000-0001-9577-0347\\
CIÊNCIA ID: 3312-D2F4-EF2F}
%\extrainfo{https://github.com/ndlopes-github}
\quote{May 2025}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle

\section{Personal Information}
\cvline{}{Full Name: Nuno David de Jesus Lopes}
\cvline{}{Date of Birth: December 31, 1976}
\cvline{}{Nationality: Portuguese}

\section{Academic Background}

\cvline{05/2014}{\textbf{PhD in Mathematics},~\emph{specialization in Numerical Analysis}, Faculty of
  Sciences and Technology, Universidade Nova de Lisboa.\newline
Advisor: Pedro Jorge da Silva Pereira\newline
Advisor: Luís Trabucho de Campos\newline
Dissertation Title:~\emph{Analytical and Numerical Methods of the Continuous and Continuous/Discontinuous Finite Element Type for the Study of Improved Boussinesq Models for Wave Propagation}}

\cvline{01/2004}{\textbf{Master’s in Mathematics},~\emph{specialization in Functional Analysis and Differential Equations}, Faculty of Sciences, Universidade de Lisboa.
% approved with a
% grade of Excellent.
\newline
  Advisor: Luís Trabucho de Campos\newline
Thesis Title: \emph{Application of the Finite Element Method in the Analysis of a Class of Convection-Diffusion Problems}}

\cvline{07/2000}{\textbf{Bachelor’s in Pure Mathematics}, Faculty of
  Sciences, Universidade de Lisboa.
% approved with
% a grade of thirteen points.
}

\section{Previous Activities and Current Situation}
\cvline{2014 -- present}{Assistant Professor at
  Instituto Superior de Engenharia de Lisboa, Instituto Politécnico de Lisboa.}
\cvline{2023 -- 2024}{Invited Assistant Professor at 
  Escola Superior de Tecnologia do Barreiro, Instituto Politécnico de Setúbal (1st semester of 2023/24).}
  
\cvline{2004 -- 2014}{Assistant Professor (2nd Three-Year Period) at
  Instituto Superior de Engenharia de Lisboa, Instituto Politécnico de Lisboa.}
\cvline{2002 -- 2004}{Assistant Professor (1st Three-Year Period) at
  Instituto Superior de Engenharia de Lisboa, Instituto Politécnico de
  Lisboa.}
\cvline{2002 -- 2002}{Assistant Professor (1st Three-Year Period) at
  Escola Superior de Tecnologia e Gestão, Instituto Politécnico de
  Bragança.}
\cvline{2001 -- 2002}{Contract Lecturer at the Faculty of Sciences and
  Technology, Universidade Nova de Lisboa.}

\subsection{Scholarships and Others}
\cvline{2007 -- 2010}{PhD Scholarship from the Instituto
  Superior de Engenharia de Lisboa, Instituto Politécnico de Lisboa, from
  February 2007 to February 2010.}
\cvline{2000 -- 2001}{Research Initiation Scholarship at the Department of
  Mathematics, Faculty of Sciences, Universidade de Lisboa, during the 2000/2001 academic year.}

\section{Research and Development Activities}
\subsection{Research Interests}
\cvline{}{Analytical and numerical methods of the finite element type for
  studying fluid mechanics models, with a particular focus on the development of Boussinesq-type models for surface wave propagation. Recently, I have also been developing research in various areas of Industrial Mathematics.}

\subsection{Involvement in Research Teams}
\cvline{2022 -- present}{Integrated member of the research team at the Computational and Stochastic Mathematics Center, Universidade de Lisboa.}
\cvline{2015 -- 2019}{Integrated member of the research team at the Mathematics and Applications Center, Universidade Nova de Lisboa.}
\cvline{2009 -- 2015}{Integrated member of the research team at the Center for Fundamental Mathematics and Applications, Universidade de Lisboa.}
\cvline{2014 -- 2015}{Collaborating member of the research team at the Mathematics and Applications Center, Universidade Nova de Lisboa.}
\cvline{2007 -- 2008}{Collaborating member of the research team at the Center for Fundamental Mathematics and Applications, Universidade de Lisboa.}

\subsection{Articles in International Peer-Reviewed Journals}
\cvline{2025}{A.~Araújo, J.~O.~Cerdeira, N.~D.~Lopes~and~A.~Moura, \emph{Minimizing costs in signal provision by communication antennas along a railway line}, 4OR-Q J Oper Res , 2025, DOI: 10.1007/s10288-025-00599-7}

\cvline{2024}{H.~B.~Oliveira~and~N.~D.~Lopes, \emph{Continuous/Discontinuous Finite Element 
Approximation of a 2D Navier-Stokes Problem Arising in Fluid Confinement}, International Journal of Numerical Analysis and Modeling, Volume 21, Number 3, Pages 315–352, 2024, DOI: 10.4208/ijnam2024-1013 }
\cvline{2023}{R. Enguiça and N.~D.~Lopes, \emph{The modeling of urban races},
Journal of Mathematics in Industry, Springer, 2023,
\url{doi:10.1186/s13362-023-00136-3}}

\cvline{2021}{N.~D.~Lopes~and~H.~B.~Oliveira, \emph{Continuous/Discontinuous
Galerkin Approximations for a Fourth-Order Nonlinear Problem}, Computers
and Mathematics with Applications,~\textbf{97}, pages 122--152, Elsevier,
{2021}.
\url{doi:10.1016/j.camwa.2021.05.034}}.% Impact factor: 3.476.}

\cvline{2015}{P.~J.~S.~Pereira,~N.~D.~Lopes,~and~L.~Trabucho,
\emph{Soliton-type and other traveling wave solutions for
an improved class of non-linear sixth-order Boussinesq equations},
Nonlinear Dynamics, Springer, 2015. \url{doi:10.1007/s11071-015-2196-9.}}
%Impact factor: 2.849.}

\cvline{2012}{N.~D.~Lopes,~P.~J.~S.~Pereira~and~L.~Trabucho, \emph{A Numerical
  Analysis of a Class of Generalized Boussinesq-Type Equations Using
  Continuous/Discontinuous FEM}, International Journal for Numerical
  Methods in Fluids,~\textbf{69} (7), pages 1186--1218, John Wiley $\&$
  Sons, Ltd, 2012. \url{doi:10.1002/fld.2631.}}% Impact factor: 1.244.}

\subsection{Book Chapters}

\cvline{2012}{N.~D.~Lopes,~P.~J.~S.~Pereira~and~L.~Trabucho, \emph{Improved
  Boussinesq Equations for Surface Water Waves}, Automated Solution of
  Differential Equations by the Finite Element Method, Eds. A. Logg,
  K.-A. Mardal, and G. N. Wells, LNCSE Volume 84, pages 471--504,
  Springer 2012. \url{doi:10.1007/978-3-642-23099-8\_25.}}

\subsection{Technical-Scientific Book}
\cvline{2019}{F.~Correia dos Santos, Jorge Duarte, N. D.~Lopes,
  \emph{Fundamentals of Numerical Analysis: with Python and R},
  2nd ed., Edições Sílabo,  2019}
\newpage
\subsection{Publications in Conference Proceedings}
\cvline{2023}{J.~E.~Marxen, T.~Charters, S.~Lopes; N.~D.~Lopes, N.~Fernandes Alves, and P.~Pascoal-Faria, \emph{An Introduction to Scaffold Design Using Topology Optimization Methods}, AIP Conference Proceedings, 2849 (1), \url{doi: 10.1063/5.0162364}}
\cvline{2023}{L.~Pinheiro, N.~Morgado, A.~Gomes, S.~Lopes, N.~D.~Lopes,
  A.~Prior, J.~Fortes, \emph{Use of Neural Networks for Improving Predictions in a Risk Alert System for Ports},
   16th Water Congress, National Laboratory for Civil Engineering, Lisbon, Portugal, 2023.}

\cvline{2023}{A.~Mendonça, B.~Machado, M.~T.~Reis, J.~Santos, C.~Fortes,
  N.~D.~Lopes, A.~Prior, \emph{Evolution of the Protective Mantle Damage of the Wave Breakwater at Ericeira Port: Probabilistic Analysis},
   16th Water Congress, National Laboratory for Civil Engineering, Lisbon, Portugal, 2023.}

\cvline{2023}{L.~Pinheiro, N.~Morgado, A.~Gomes, S.~Lopes, N.~D.~Lopes,
  A.~Prior, J.~Fortes, \emph{Neural Networks for Optimization of an Early Warning System for Moored Ships in Harbours},
   ICCE 2022, 37th International Conference on Coastal Engineering,
   December, 2022. \url{doi:10.9753/icce.v37.papers.60}}

\cvline{2012}{N.~D.~Lopes,~P.~J.~S.~Pereira~and~L.~Trabucho, \emph{A
    Numerical Analysis of a Class of KdV-BBM Equations Using
    Continuous/Discontinuous Galerkin Finite Element Method},
  Proceedings of MEFTE 2012, IV National Conference on Fluid Mechanics,
  Thermodynamics, and Energy, National Laboratory for Civil Engineering, Lisbon, Portugal, 2012.}

\cvline{2011}{N.~D.~Lopes,~P.~J.~S.~Pereira~and~L.~Trabucho, \emph{A Numerical Method for a Class of Boussinesq Equations for Surface Waves with Time-Dependent Bathymetry}, Bulletin of the SPM--National Meeting of the SPM 2010, pages 42-46, 2011.}

\cvline{2010}{N.~D.~Lopes,~P.~J.~S.~Pereira~and~L.~Trabucho, \emph{A C/DG-FEM Solution of an Improved Boussinesq System for Surface Water Waves},
  Proceedings of the Fifth European Conference on CFD, ECCOMAS CFD 2010,
  National Laboratory for Civil Engineering, Lisbon, Portugal, 2010.}

\cvline{2004}{N.~D.~Lopes~and~L.~Trabucho, \emph{Application of the Finite Element Method in the Analysis of a Class of Convection-Diffusion Problems}, Computational Methods in Engineering Congress,
  National Laboratory for Civil Engineering, Lisbon, Portugal, 2004.}

\subsection{Software Development}
\cvline{2010 -- 2015}{\emph{DOLFWAVE: A Library for Surface Water Waves
    Problems}, \textrm{http://launchpad.net/dolfwave}, with scientific supervision by~P.~J.~S.~Pereira~ and~L.~Trabucho.
  }
\subsection{Conference Organizing Committees}
%% \cvline{2020}{Member of the local organizing committee of the national conference: \emph{Workshop FromIndustry -- preESGI 2020}
%%   jointly organized with the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN,
%%   Instituto Superior de Engenharia de Lisboa, April 28, 2020, Lisbon, Portugal.}
\cvline{2024}{Member of the organizing committee of the international conference: \emph{amim'24: autumn meeting for industrial mathematics}, October 4-5, 2024, Foz do Arelho, Portugal.}

\cvline{2023}{Member of the organizing committee of the national conference: \emph{MATH'23: Networking Workshop}, Instituto Superior de Engenharia de Lisboa, May 11-12, 2023, Lisbon, Portugal.}

\cvline{2022}{Member of the local organizing committee of the international conference: \emph{ESGI161}, jointly organized with the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN, Instituto Superior de Engenharia de Lisboa, September 4-9, 2022, Lisbon, Portugal.}

\cvline{2022}{Member of the organizing committee of the national conference: \emph{LMATE'22: Networking Workshop}, organized by the coordinating committee of LMATE-ISEL, Instituto Superior de Engenharia de Lisboa, May 5-6, 2022, Lisbon, Portugal.}

\cvline{2020}{Member of the local organizing committee of the national conference: \emph{Workshop FromAcademy -- preESGI 2020}, jointly organized with the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN, Instituto Superior de Engenharia de Lisboa, January 22, 2020, Lisbon, Portugal.}

\subsection{Conference Scientific Committees}
\cvline{2024}{
  Member of the scientific committee of the international conference:
  \emph{ESGI181}, organized by the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN, July 8-12, 2024, UTAD, Vila Real, Portugal.}
\cvline{2023}{
  Member of the scientific committee of the international conference:
  \emph{ESGI174}, organized by the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN, July 3-7, 2023, ESTG-IPP, Felgueiras, Portugal.}

\cvline{2018} {Member of the scientific committee of the international conference: \emph{Mathematics for Smart Security: Challenges and
  Opportunities}, organized by the Portuguese network for Mathematics in Industry and Innovation -- PT-MATHS-IN,
  Instituto Superior de Engenharia de Lisboa, October 19, 2018, Lisbon, Portugal.}

\subsection{Oral Presentations at Conferences and Seminars}
\cvline{2024}{N.~D.~Lopes, "CD-FEM solutions of fourth-order nonlinear models for the confinement of fluid flows", International Conference Mathematical Analysis and Applications in Science and Engineering: ICMASC24, June 20-22, Instituto Superior de Engenharia do Porto, Porto, Portugal.}

\cvline{2022}{N.~D.~Lopes, ``Alguns métodos e resultados numéricos sobre o confinamento de um fluido, a injecção assistida por água num molde e corridas urbanas'', Seminário de Física e Matemática, Departamento de Física, Instituto Superior de Engenharia de Lisboa, May 2, 2022.}

\cvline{2021}{N.~D.~Lopes, ``C/DG-FEM solutions of a fourth-order nonlinear model for the confinement of fluid flows'', joint work with H.~B.~de~Oliveira, Encontro Nacional da Sociedade Portuguesa de Matemática 2021, July 16, 2021.}

\cvline{2020}{E.~C.~Figueiredo (speaker), N.~D.~Lopes, Ricardo Enguiça, Tiago Charters de Azevedo, Rui Silva, Bruno Mendes, Artur Mateus, Nuno Alves and Paula Pascoal-Faria, ``MathMould I\&D Project: Analytical and Numerical Methods in Water Assisted Injection in Multi--Tubular Moulds'', poster with oral presentation by E.~C.~Figueiredo at RESIM -- Research on Sustainable and Intelligent Manufacturing, International Virtual Conference, Politécnico de Leiria and Universitat Internacional de Catalunya, June 4-5, 2020.}

\cvline{2017}{N.~D.~Lopes, ``Analytical and Numerical Methods for some Improved Boussinesq Models for Surface Water Waves'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Seminário de Análise do Centro de Matemática e Aplicações do Departamento de Matemática da Faculdade de Ciências e Tecnologia da Universidade Nova de Lisboa, March 15, 2017, Almada, Portugal.}

\cvline{2015}{N.~D.~Lopes, ``Analytical and Numerical Methods of the type FEM-C/D for Improved Boussinesq Models'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Seminário de Matemática Aplicada e Análise Numérica do Centro de Matemática e Aplicações do Instituto Superior Técnico, July 16, 2015, Lisbon, Portugal.}

\cvline{2012}{N.~D.~Lopes, ``FEM solutions of some Boussinesq-type models for surface water waves'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Seminários do Centro de Matemática da Universidade de Coimbra, July 11, 2012, Coimbra, Portugal.}

\cvline{2012}{N.~D.~Lopes, ``A numerical analysis of a class of KdV-BBM equations using Continuous/Discontinuous Galerkin Finite Element Method'', joint work with P.~J.~S.~Pereira and L.~Trabucho, MEFTE 2012, IV Conferência Nacional em Mecânica dos Fluidos, Termodinâmica e Energia, May 28-29, 2012, Laboratório Nacional de Engenharia de Lisboa, Lisbon, Portugal.}

\cvline{2011}{N.~D.~Lopes, ``Solutions of some improved Boussinesq-type models for surface water waves using finite element methods'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Recent trends in hyperbolic and related PDEs: Theory, numerics and applications, October 21, 2011, Instituto para a Investigação Interdisciplinar, Universidade de Lisboa, Lisbon, Portugal.}

\cvline{2011}{N.~D.~Lopes, ``A C/DG-FEM solution of an improved fourth-order Boussinesq model for surface water waves'', joint work with P.~J.~S.~Pereira and L.~Trabucho, First European Meeting of PhD Students in Mathematics, June 28-29, 2011, LAMFA, Université de Picardie Jules Verne, Amiens, France.}

\cvline{2011}{N.~D.~Lopes, ``DOLFWAVE: a FEniCS Application for Water Waves Simulation'', joint work with P.~J.~S.~Pereira and L.~Trabucho, SIAM Conference on Mathematical and Computational Issues in the Geosciences, March 21-24, 2011, Long Beach, United States of America.}

\cvline{2010}{N.~D.~Lopes, ``Um método numérico para uma classe de equações de Boussinesq para ondas de superfície com batimetria dependente do tempo'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Encontro Nacional da SPM 2010, July 8-10, 2010, Leiria, Portugal.}

\cvline{2010}{N.~D.~Lopes, ``A C/DG-FEM Solution of an Improved Boussinesq System for Surface Water Waves'', joint work with P.~J.~S.~Pereira and L.~Trabucho, Fifth European Conference on CFD, ECCOMAS CFD 2010, June 14-17, 2010, Laboratório Nacional de Engenharia de Lisboa, Lisbon, Portugal.}

\cvline{2010}{N.~D.~Lopes, ``DOLFWAVE - Use of FEniCS for surface waves modelling'', joint work with P.~J.~S.~Pereira and L.~Trabucho, CBC Workshop on Tsunami Modelling, June 3-4, 2010, Center of Biomedical Computing, Simula Research Laboratory, Oslo, Norway.}

\cvline{2009}{N.~D.~Lopes, ``Aplicações do Método dos Elementos Finitos a uma Classe de Sistemas de Boussinesq'', joint work with P.~J.~S.~Pereira and L.~Trabucho, seminário do Centro de Matemática e Aplicações, January 21, 2009, Universidade Nova de Lisboa, Monte de Caparica, Portugal.}

\cvline{2004}{N.~D.~Lopes, "Aplicação do Método dos Elementos Finitos na Análise de uma Classe de Problemas Convecção-Difusão", joint work with L.~Trabucho, Congresso de Métodos Computacionais em Engenharia, May 31 - June 2, 2004, Laboratório Nacional de Engenharia Civil, Lisbon, Portugal.}

\cvline{2003}{N.~D.~Lopes, "Análise Numérica de um Modelo de Convecção-Difusão: Aplicação ao Estuário do Tejo", joint work with L.~Trabucho, Seminários de Análise Funcional, Equações Diferenciais e Análise Numérica, February 6, 2003, Centro de Matemática e Aplicações Fundamentais da Universidade de Lisboa, Lisbon, Portugal.}

\cvline{2001}{N.~D.~Lopes, "O Método dos Elementos Finitos numa equação de Convecção-Difusão", joint work with L.~Trabucho, Seminários de Análise Funcional, Equações Diferenciais e Análise Numérica, December 20, 2001, Centro de Matemática e Aplicações Fundamentais da Universidade de Lisboa, Lisbon, Portugal.}

\subsection{Participation in the \emph{European Study Groups with Industry}}

\cvline{2024}{Collaborator in the group: \emph{Enhancing Wine Sensory Evaluation: Developing a Robust System for Consistent and Accurate Taster Scores}, problem presented by the Viticulture Commission of the Vinho Verde Wine Region in the \textit{181st European Study Group with Industry}, 2024, UTAD, Vila Real, Portugal.}

\cvline{2023}{Collaborator in the group: \emph{Optimization of Sole Production Scheduling}, problem presented by SoftIdea in the \textit{174th European Study Group with Industry}, 2023, ESTG-IPP, Felgueiras, Portugal.}

\cvline{2022}{Collaborator in the group: \emph{Optimal Site Positioning}, problem presented by Solvit in the \textit{161st European Study Group with Industry}, 2022, ISEL-IPL, Lisbon, Portugal.}

\cvline{2019}{Collaborator in the group: \emph{Vipex Container Lid}, problem presented by Vipex in the \textit{155th European Study Group with Industry}, 2019, Escola Superior de Saúde of the Polytechnic Institute of Leiria, Leiria, Portugal.}

\cvline{2018}{Collaborator in the group: \emph{Managing start waves for mass running events}, problem presented by Lap2Go in the \textit{140th European Study Group with Industry}, 2018, Escola de Tecnologia of the Polytechnic Institute of Setúbal, Barreiro, Portugal.}

\cvline{2008}{Collaborator in the group: \emph{Cooling of a rotor}, problem presented by BioSafe in the \textit{65th European Study Group with Industry}, Faculty of Engineering, University of Porto, 2008, Porto, Portugal.}

\cvline{2007}{Collaborator in the group: \emph{Brisa}, problem presented by Brisa in the \textit{60th European Study Group with Industry}, ISEL, 2007, Lisbon, Portugal.}

\subsection{Technical-Scientific Reports}

\cvline{2024\\ ESGI174}{A. Moura, I. Lopes, J. Matias, N. Lopes, and R. Enguiça, \emph{Optimization of Sole Production Scheduling}, problem presented by SoftIdea at the 174th European Study Group with Industry (2023), Cambridge Open Engage, Mathematics in Industry Reports, 2024, DOI: {10.33774/miir-2024-zhmg5}.}

\cvline{2022\\ ESGI161}{A. Araújo, J. O. Cerdeira, N. Lopes, A. Moura, and E. Silva, \emph{Optimal Site Positioning}, problem presented by Solvit at the 161st European Study Group with Industry (2022), Cambridge Open Engage, Mathematics in Industry Reports, 2023, DOI: {10.33774/miir-2023-tkf3c}.}

\cvline{2019\\ ESGI155}{N. Ferreira, N. Alves, N. Lopes, P. Faria, and R. Barreira: \emph{Vipex Container Lid}, problem presented by Vipex at the 155th European Study Group with Industry, reports of the Portuguese Study Groups, 155th European Study Group with Industry, 1 to 5 July, 2019, School of Health, Polytechnic Institute of Leiria, Leiria, Portugal.}

\cvline{2018\\ ESGI140}{P. Amaral, S. Barbeiro, R. Barreira, M. Cruz, R. Enguiça, N. Lopes, M. McPhail, and F. Wechsung: \emph{Managing Start Waves for Mass Running Events}, problem presented by Lap2Go, reports of the Portuguese Study Groups, 140th European Study Group with Industry, 4 to 8 June, 2018, Barreiro School of Technology, Polytechnic Institute of Setúbal, Barreiro, Portugal.}

\cvline{2015\\ \textbf{W{\"{u}}rth Portugal}}{N. D. Lopes, \emph{Profitability Optimization in Supply Chain: Problem presented by W{\"{u}}rth Portugal to the Department of Mathematics, Instituto Superior de Engenharia de Lisboa}, November 2015.}

\cvline{2008\\ ESGI65}{I. Cruz, P. Freitas, and N. D. Lopes, \emph{Cooling of a Rotor}, problem presented by BioSafe, reports of the Portuguese Study Groups, 65th European Study Group with Industry, 21 to 24 April, 2008, Centre of Mathematics, University of Porto, Portugal.}

\subsection{Scientific Projects}

\cvline{2022 -- 2023}{Team member with research role in the project \emph{3A}, Research, Development, Innovation, and Artistic Creation project of the Polytechnic Institute of Lisbon (IDI$\&$CA), ref.: IPL/2022/3A\_ISEL.}

\cvline{2019 -- 2020}{Coordinator of the project \emph{MathMould}, Research, Development, Innovation, and Artistic Creation project of the Polytechnic Institute of Lisbon (IDI$\&$CA), ref.: IPL/2019/MathMould\_ISEL.}

\cvline{2013 -- 2014}{Team member with research role in the project PEst-OE/MAT/UI0209/2013, Strategic Project - UI 209 - 2013-2014.}

\cvline{2011 -- 2012}{Team member with research role in the project PEst-OE/MAT/UI0209/2011, Strategic Project - UI 209 - 2011-2012.}

\cvline{2005 -- 2009}{Team member with research role in the project POCI/MAT/60587/2004, Asymptotic Analysis Applied to the Mechanics of Continuous Media, FCT.}

\subsection{Community Cooperation Projects}

\cvline{2015}{Technical-scientific advisor for the \emph{Profitability Optimization Project} associated with the \emph{Service Contract of ISEL to W{\"{u}}rth} Portugal, September to December 2015.}

\newpage
\subsection{Internship Supervisions in the Context of Industrial Mathematics}

\cvline{2025\\ \textbf{Iber-Oleff}}{ João Domingos, "Estudo sobre o ´Indice de Conforto Acústico (IAC) em Ventiladores de Ar Automóvel", hosting institution: Iber-Oleff, grade 15,
undergraduate internship in Applied Mathematics to Technology and Business (LMATE),
 joint supervision with Mihail Fontul (\textbf{Iber-Oleff}),
 Tiago Charters de Azevedo (ISEL), February 2025,
 Department of Mathematics, Instituto Superior de Engenharia de Lisboa.
}

\cvline{2024\\ \textbf{SOLVIT}}{Inês Henriques, ``Railway Signal Monitoring: An Algorithmic Approach for Improved Maintenance Strategies'', hosting institution: SOLVIT, grade 18, Master's thesis in Applied Mathematics to Industry (MMAI), joint supervision with  Nuno Cota (\textbf{SOLVIT}),  Filipe Cal (ISEL), November 2024, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2023\\ \textbf{LNEC}}{Bernardo Machado, ``Numerical Modeling of Breakwaters for Slopes and Marginal Protection Structures. Case Studies: Sines Fishing Port and Praia da Vitória Port'', hosting institution: LNEC Portugal, grade 18, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with Ana Mendonça (\textbf{LNEC}), Ana Filipa Prior (ISEL), September 2023, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2022\\ \textbf{LNEC}}{Nuno Moreira Morgado, ``Calibration of the SWAN Numerical Model Based on Neural Networks'', hosting institution: LNEC Portugal, grade 16, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with Liliana Pinheiro (\textbf{LNEC}),  Ana Filipa Prior (ISEL), July 2022, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2022\\ \textbf{SANDO-\\METAL}}{Inês Morais, ``Acoustic Behavior Model in Air Treatment Units'', hosting institution: Sandometal, grade 16, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with  Rui Santos, (\textbf{Sandometal}),  Pedro Silva (\textbf{Sandometal}),  Sérgio Lopes (ISEL), March 2022, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2021\\ \textbf{CDRSP-IPLeiria}}{Jan Marxen, ``An Introduction to Scaffold Design Using Topology Optimization Methods'', \emph{CDRSP}, grade 20, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with Paula Pascoal-Faria (CDRSP), Sérgio Lopes (ISEL), Tiago Charters de Azevedo (ISEL), July 2021, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2021\\ \textbf{LNEC}}{Catarina Marques Graça, ``Validation of the SWAN Numerical Model Based on Statistical Comparison of Sea State Regimes'', hosting institution: LNEC Portugal, grade 18, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with  Liliana Pinheiro (\textbf{LNEC}),  Ana Filipa Prior (ISEL), March 2021, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2020\\ \textbf{CDRSP-IPLeiria}}{Eurico Carnall Figueiredo, ``An Introduction to Analytical and Numerical Methods for Computational Fluid Dynamics Simulation: Application to Water Assisted Injection Molding (WAIM)'', hosting institution: \emph{CDRSP}, grade 17, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with  Paula Pascoal-Faria (CDRSP), Ricardo Enguiça (ISEL),  Tiago Charters de Azevedo (ISEL), July 2020, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2020\\ \textbf{GALP}}{Diogo Joaquim, ``Predictive Modeling of Consumption in the Natural Gas Market of Portugal and Spain'', hosting institution: \emph{GALP Portugal}, grade 18, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with  Ricardo Enguiça (ISEL), Gonçalo Monteiro (GALP), July 2020, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2020 \\ \textbf{LNEC}}{Ana Rita Costa, ``Analysis of the Operationality of the Port Terminal of S. Roque do Pico, Based on the General Sea State Regime'', hosting institution: \emph{LNEC}, grade 16, undergraduate internship in Applied Mathematics to Technology and Business (LMATE), joint supervision with Sandra Aleixo (ISEL),  Juana Fortes (LNEC), Liliana Pinheiro (LNEC), February 2020, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2019\\ \textbf{GALP}}{Ruben Sales, ``Stock and Contracting Optimization and Capacity Planning'', hosting institution: GALP Portugal, grade 16, Bachelor's thesis in Applied Mathematics to Technology and Business (LMATE), joint supervision with Ricardo Enguiça (ISEL), Gonçalo Monteiro (GALP), July 2019, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2019 \\ \textbf{W{\"{u}}rth} Portugal}{Pedro Ferreira, ``Optimization of Prices and Margins, W{\"{u}}rth Portugal'', grade 15, Bachelor's thesis in Applied Mathematics to Technology and Business (LMATE), joint supervision with Tiago Charters de Azevedo (ISEL), Dr. Gonçalo Figueiredo (W{\"{u}}rth Portugal) and Dr. Jorge Fernandes (W{\"{u}}rth Portugal), July 2019, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\section{Pedagogical and Organizational Activities}
\subsection{Committees and Other Management Positions}
\cvline{2018 -- 2022
  \phantom{a}[ISEL-IPL]
}
{ Member of the Coordinating Committee of the Bachelor's Degree in Applied Mathematics to Technology and Business (CCLMATE), from June 2018 to May 2023.}

\cvline{2018 -- 2024
  \phantom{a}[ISEL-IPL]
}
{Responsible for the LMATE part of the \emph{LAB4MAT}, computational laboratory of LMATE, since October 17, 2018.}

\cvline{2018 [ISEL-IPL]}{Member of the Founding Committee of the Digital Workshop (ODI), Instituto Superior de Engenharia de Lisboa, 2018.}

\subsection{Teaching Functions}
\cvline{2002 -- present \phantom{a}[ISEL-IPL]}{Teaching (and/or lecturing) in a theoretical-practical regime of the following courses:
  \begin{itemize}
  \item Linear Algebra and Analytical Geometry;
  \item Mathematical Analysis I;
  \item Mathematical Analysis II;
  \item Vector Analysis;
  \item Numerical Analysis;
  \item Differential and Integral Calculus;
  \item Differential and Integral Calculus II;
  \item Numerical Calculus;
  \item Complementary Mathematical Analysis;
  \item Introduction to Numerical Analysis;
  \item Applied Mathematics to Civil Engineering;
  \item Applied Mathematics to Electrical Engineering;
  \item Mathematical Modeling Seminar;
  \end{itemize}
  at the Instituto Superior de Engenharia de Lisboa, Instituto Politécnico de Lisboa.}

\cvline{2002 -- 2002 [ESTG-IPB]}{Teaching in a practical regime of the courses of Mathematical Analysis I and Linear Algebra and Analytical Geometry, Escola Superior de Tecnologia e Gestão, Instituto Politécnico de Bragança.}

\cvline{2001 -- 2002 \phantom{a}[FCT-UNL]}{Teaching in a practical regime of the course Mathematical Analysis I at the Faculdade de Ciências e Tecnologia, Universidade Nova de Lisboa.}

\cvline{2000 -- 2001 [FC-UL]}{Teaching in a practical regime of the courses Algebra and Applications I and II at the Faculdade de Ciências, Universidade de Lisboa.}

\newpage
\subsection{Course Support Texts}
\cvline{2017}{N.~D.~Lopes, \emph{Numerical Methods: Practical Notes}, Course of Introduction to Numerical Analysis in the Bachelor's Degree in Applied Mathematics to Technology and Business at the Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2016}{N.~D.~Lopes, \emph{Introduction to Numerical Calculus with Python}, Course of Numerical Calculus in the Bachelor's Degree in Chemical and Biological Engineering at the Department of Chemical Engineering, Instituto Superior de Engenharia de Lisboa.}

\cvline{2016}{N.~D.~Lopes, R. Enguiça, I. Coelho, and P. Simões, \emph{Elementary Functions - I}, Course of Elementary Functions - I for the "Maiores de 23" preparatory course at the Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2015}{N.~D.~Lopes, \emph{Introduction to Numerical Calculus with Python}, Course of Numerical Calculus in the Bachelor's Degree in Chemical and Biological Engineering at the Department of Chemical Engineering, Instituto Superior de Engenharia de Lisboa.}

\subsection{Jury}
\cvline{2024}{Member (arguer) of the Master's Exam Jury of Cristian Robu. Professional Internship Report performed at “Infraestruturas de Portugal”, titled “The Use of Artificial Intelligence in the Recognition of Railway Assets Based on High-Resolution Drone Images”, classification of 18 (eighteen) points.}

\cvline{2024}{Member of jury for competition \# 4603 for the award of two Research Initiation Grants (BII) at FCiências.ID - Associação Para a Investigação e Desenvolvimento de Ciências, within the project “UIDP/04621/2020”, \url{doi:10.54499/UIDP/04621/2020}.}

\cvline{2023}{Member of jury for PhD scholarship in the area of Digitalization and Artificial Intelligence -- Computer Science/Mathematics, awarded under the Collaboration Protocol for the Financing of the Multiannual Plan of Research Scholarships for Doctoral Students, signed between FCT and IPS. Announcement of January 25, 2023, IPS.}

\cvline{2022}{Member of jury for competition for the award of a Research Initiation Grant, reference \url{IPL/2022/3A\_ISEL/BII/5M}, within the Scientific and Technological Research Project 3A-AdaptiveAllocApp, fully funded by the Institute of Polytechnic of Lisbon.}

\cvline{2022}{President of jury for competition for the award of a Research Initiation Grant, reference \url{IPL/2022/3A\_ISEL/BII/4M}, within the Scientific and Technological Research Project 3A-AdaptiveAllocApp, fully funded by the Institute of Polytechnic of Lisbon.}

\cvline{2022}{President of jury for the internship defense of Maria Silva, LMATE Internship-- \emph{Milestone}, July 26, 2022, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2021}{Arguer for the internship defense of Ricardo Dias, LMATE Internship-- \emph{Arquiled}, July 2021, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2020}{President of jury for the internship defense of Carolina Figueiredo, LMATE Internship--AdTA, February 13, 2020, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2020}{President of jury for the internship defense of Catarina Ferreira, LMATE Internship--CML, February 11, 2020, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\cvline{2019}{President of jury for the internship defense of Rafaela Couchinho, LMATE Internship--GALP, July 9, 2019, Department of Mathematics, Instituto Superior de Engenharia de Lisboa.}

\subsection{Scientific Promotion and Dissemination Activities}
\cvline{2018}{N. D. Lopes, ``Waves, Pollutants and Turbulence'', communication at the Open Week of Instituto Superior de Engenharia de Lisboa, February 20-23, 2018.}

\cvline{2017}{N. D. Lopes and N. Santos, ``Mathematics in Big Wave Surfing -- Forecasting and Modeling'', invited lecture at the Summer School of the Portuguese Mathematical Society $\&$ Mat\-Oeste 2017 -- Mathematics of the Sea, ESTG, Instituto Politécnico de Leiria, July 13, 2017.}

\cvline{2017}{N. D. Lopes, ``Some Analytical and Numerical Models for the Generation and Propagation of Surface Ocean Waves'', invited communication at the lecture ``Our Oceans, Our Future'', Instituto Superior de Engenharia de Lisboa, June 22, 2017.}

\cvline{2016}{N. D. Lopes, ``Introduction to Python for LMATE'', seminar in the Bachelor's course in Mathematics Applied to Technology and Business, Instituto Superior de Engenharia de Lisboa, October 12, 2016.}

\cvline{2015}{N.D. Lopes, ``Some Numerical Simulations with the Finite Element Method: Convection-Diffusion; Boussinesq; Navier-Stokes'', lecture in the Computational Fluid Mechanics course, Instituto Superior de Engenharia de Lisboa, by invitation of  Pedro Patrício, December 10, 2015.}

\cvline{2015}{Collaboration at the Department of Mathematics stand at the ``Science and Technology Fair at ISEL'', exhibiting numerical simulations resulting from research work in Fluid Mechanics models, November 25, 2015.}

\cvline{2015}{Collaboration at the ``DIY'' stand, organized by  Tiago Charters de Azevedo, at the ``Science and Technology Fair at ISEL'', exhibiting an audio synthesizer, November 25, 2015.}

\cvline{2015, 2016}{Collaboration as a representative of the Department of Mathematics of Instituto Superior de Engenharia de Lisboa at the 2015 and 2016 editions of the ``Futurália'' fair in Lisbon.}

\cvline{2010, 2011, 2012}{N.~D.~Lopes, ``Waves, Pollutants and Turbulence'', science dissemination seminar at the events: \emph{MatNova 2012}, \emph{Mathematics at FCT 2011}, and \emph{ExpoFCT 2010}, Faculty of Sciences and Technology, Universidade Nova de Lisboa.}

\cvline{2004, 2005}{N.~D.~Lopes, ``Numerical Analysis of a Convection-Diffusion Model: Application to the Tagus Estuary'', science dissemination seminar at the courses \emph{Mathematics Alpha 2004} and \emph{Mathematics Alpha 2005}, Faculty of Sciences, Universidade de Lisboa.}

\section{Other Information}
\cvline{}{Programming Languages: Python, Julia, C++.}
\cvline{}{Languages: English (good levels of reading, writing, and conversation).}

\end{document}
